\subsection{ Technical Feasibility}

To conduct this project knowledge base in the field of image processing and mathematics is required, to build on the knowledge in artificial intelligence, the use of generative adversarial neural networks and supervised learning to build and improve the models that perform the tasks of source separation. Also experience in web designing and launching to represent our product to any user or organization, So that they buy it. We used our devices to train the models besides the online free service; Google Colab. \\ 
Sufficient attempts were made in the field of MSS solutions that performed well on the problem. Additionally most of the developed models were guided by published research papers, Therefore indicating and emphasize the feasibility of the solution.

\subsection{ Operational Feasibility }

As mentioned before we deal with two types of users, One uses the application for special purposes; finding missing people or identifying the image of some ancient king or queen, so they need to have at least one PC with VRAM 11GB or more, to be able to run the application which will cost around 1500\$ to 2000\$ or more depends on the number of PCs will be used and their specifications. For the other type of users we can deploy the app for free as a trial, Then a little expense is asked from subscribed users so that the deployment cost is covered with profits. 

\subsection{ Legal Feasibility }

The development of the project depends on publicly available libraries and software tools, like pytorch, flask and vuejs. All the pretrained models used are open sources and legal to be used for any product. All Datasets used to train any written model are public for any commercial use, or made by us. The devices used to train those models are our own or on Google Colab which is also public for any use.

\subsection{ SWOT Analysis }

\subsubsection{ \emph{Strength S} }

\begin{itemize}
    \item Fast.
    \item Automated.
    \item Easy-to-use.
    \item Realistic Results.
    \item Containing a Sufficient set of features to describe a human face.
\end{itemize}

\subsubsection{ \emph{Weaknesses W} }

\begin{itemize}
    \item Facial Features Entanglement.
    \item High VRAM Usage.
    \item Sometimes Results can be inaccurate.
\end{itemize}

\subsubsection{ \emph{ Opportunities O}} 

\begin{itemize}
    \item No Competitors.
    \item Fast and Automated.
\end{itemize}

\subsubsection{\emph{Threats T} }

\begin{itemize}
    \item Lake of Datasets.
    \item High Cost.
\end{itemize}