
Face Generation is an important field in the market, it is used widely in all camera applications to apply filters on the taken images most of the usage was for entertainment, Although it can be used to have photos for any missing people or criminal and that will increase the chance to find that missing people or the criminal.
 
\subsection{Targeted Customers}
Our Project is directed to all governmental and volunteering organizations, that need to generate identical faces of missing people from bare human description of their facial features.
It also can be used to identify the ancient kings and queens faces from the Papyrus .
We can categorize the different target companies into the following:
\begin{itemize}
    \item \textbf{Criminal identification from witnesses descriptions :}
        \begin{itemize}
            \item INTERPOL.
            \item Different Police Stations.
        \end{itemize}
    \item \textbf{Missing People organizations like :}
        \begin{itemize}
            \item International Center for Missing and Exploited Children.
            \item International Red Cross and Red Crescent Movement.
            \item International Commission on Missing Persons \emph{ICMP}
            \item The Doe Network.
            \item National Missing and Unidentified Persons System.
            \item Missing Persons Support Center.
            \item LostMissing Inc.
            \item Missing People In America.
            \item Be United Missing Persons Inc.
            \item others.
        \end{itemize}
    \item \textbf{Historical Characters Identification :}
        \begin{itemize}
            \item Archaeological and Historical Research Facilities.
        \end{itemize}
\end{itemize}

\subsection{Market Survey}

As mentioned previously, most Applications that uses face generation is for entertainment, So they depends only on image refinement on limited number of features to generate the image unlike us, We have both image generation and refinement using 32 features for generation and 38 for refinement.
Besides that our goal is to find missing person for purpose more important than entertaining. Our biggest competitor is FaceApp, followed by PicsArt, Facetune2 and Booth Apps.
  

\subsubsection{FaceAPP}
\emph{FaceAPP} is considered Image and video editing mobile application, it generates highly realistic transformations of human faces in photographs using AI and Neural Networks. 
The Limitation of the App compared with us, it only used for refinement using 14 facial feature which may be not enough for generating face from scratch.

\subsubsection{PicsArt}

\subsubsection{Facetune2}

\subsubsection{Booth Apps}

\subsection{Business Case and Financial Analysis }
